Relative parabolic factorizations of Chevalley groups

### 2015-04-16 bass-kolster.tex
Bass-Kolster for B_l finished

\textsc{Case $\Phi=\rB_\ell$:}
Let $(1+r_1,r_2,\dots,r_\ell,r_0,r_{-\ell},\dots,r_{-1})^t\in\Ums(2\ell+1,R,I)$ be the first column of $g$. Find $c_1,\dots,c_\ell\in I$ (\textbf{can we?}) such that $(1+r_1+c_1r_0,\dots,r_\ell+c_\ell r_0,r_{-\ell},\dots,r_{-1})$ is unimodular. Apply $x_{\beta_k}(c_k)$ with $\beta_k=\alpha_k+\dots+\alpha_\ell$ for all $k=1,\dots,\ell$, and denote the resulting column by $(1+r_1',\dots,r'_{-1})^t$. Note that $r'_i$ is not necessary equal to $r_i+c_ir_0$. Denote also $\mathfrak{a}=r_{-\ell}R+\dots+r_{-1}R$, then one has $r'_{-\ell}R+\dots+r'_{-1}R=\mathfrak{a}$ and the ideal, generated by $1+r'_1,\dots,r'_\ell$ and $\mathfrak{a}$, is the whole $R$.

@@

Since $\asr(R,I)\leqslant\ell$, there exist $c_{-\ell},\dots,c_{-2}$ such for $\mathfrak{b}=\langle s_{-\ell}+c_{-\ell}s_{-1},\dots,s_{-2}+c_{-2}s_{-1}\rangle$ one has $\mathfrak{I}(\mathfrak{b})=\mathfrak{I}(\mathfrak{a})$.
\end{proof}

>>>>

\textsc{Case $\Phi=\rB_\ell$:}
Let $(1+r_1,r_2,\dots,r_\ell,r_0,r_{-\ell},\dots,r_{-1})^t\in\Ums(2\ell+1,R,I)$ be the first column of $g$. Find $c_1,\dots,c_\ell\in I$ such that $(1+r_1+c_1r_0,\dots,r_\ell+c_\ell r_0,r_{-\ell},\dots,r_{-1})$ is unimodular. Apply $x_{\beta_k}(c_k)$ with $\beta_k=\alpha_k+\dots+\alpha_\ell$ for all $k=1,\dots,\ell$, and denote the resulting column by $(1+r_1',\dots,r'_{-1})^t$. Note that $r'_i$ is not necessary equal to $r_i+c_ir_0$. Denote also $\mathfrak{a}=r_{-\ell}R+\dots+r_{-1}R$, then one has $r'_{-\ell}R+\dots+r'_{-1}R=\mathfrak{a}$ and the ideal, generated by $1+r'_1,\dots,r'_\ell$ and $\mathfrak{a}$, is the whole $R$.

@@

Since $\asr(R,I)\leqslant\ell-1$, there exist $c_{-\ell},\dots,c_{-2}$ such for
\[ \mathfrak{b}=\langle s_{-\ell}+c_{-\ell}s_{-1},\dots,s_{-2}+c_{-2}s_{-1}\rangle=\langle s'_{-\ell},\ldots,s'_{-2}\rangle \]
one has $\mathfrak{I}(\mathfrak{b})=\mathfrak{I}(\mathfrak{a})$. So $(1+s_1,s'_{-\ell},\ldots,s'_{-2})^t\in\Ums(\ell,R,I)$ and can be shortened to some $(1+s''_1,s''_{-\ell},\ldots,s''_{-3})\in\Ums(\ell-1,R,I)$ with the help of $x_{\beta_i}$, $\beta_i=\alpha_2+\ldots+\alpha_i$, and $x_{\alpha_{\max}}$. Then one use $z_{\alpha_{\max}}$ to put $s''_1$ in position $-2$ and repeat endging of the previous cases.
\end{proof}
